Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-04-26 paper.tex
edits in Sect 2.2
edits in Sect 2

\renewcommand{\vec}{\ensuremath{\mathbfit}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Vph}{V_\mathrm{ph}}
\newcommand{\mug}{\umu G}
\newcommand{\RH}{R_\rmn{RH}}
\newcommand{\bvel}{\ensuremath{\boldsymbol{\varv}}}
\newcommand{\bnabla}{\ensuremath{\boldsymbol{\nabla}}}
\newcommand\eb{\epsilon_\rmn{B}}
\newcommand{\dps}{\displaystyle}

@@

During post-processing of our Coma-like cluster simulation, we solve
the Fokker-Planck equation over a redshift interval from $z=5$ to
0. The simulated cluster undergoes a major merger over the last
1-2~Gyrs that is thought to inject large turbulent eddies. Following
standard approaches
\citep{brunetti07,brunetti11,2004ApJ...614..757Y,2015ApJ...800...60M}
we assume that about one Gyr after core passage the fields have
decayed down to the smallest scales where reacceleration is most
efficient ($D_{pp}\sim k_\rmn{cut}$) and the radio halo turns on
shortly after. Note that the exact decay time of the turbulens is of
minor importance, since the thermal and CR quantities are very similar
a few 100 Myrs before and after $z=0$ where we have chosen to evaluate
the simulations. This delay naturally explains why giant radio halos
are only seen in a fraction of all merging clusters. In all our
calculations we assume that turbulent reacceleration efficiently
accelerates particles for $\tau_\rmn{cl}\sim650$~Myrs (which is
roughly the cascade time on which turbulence is damped) and that
during this turbulent phase CR streaming and spatial diffusion can be
neglected. In our \Mstream model, CR streaming and diffusion are
incorporated separately during kinematically quiescent times that
precede the merger. As a result, flat CRp profiles are produced on
relatively short timescales ($\sim 0.1-0.5$ Gyr). This allows us to
implicitly solve for CR streaming in our calculations, where we adopt
a toy model that enforce a flat CRp profile at all quiescent times
\citep{wiener13}. We assume that CRs cannot stream significantly past
perpendicular $B$-fields at the accretion shock, so that the total
number of CRs is conserved within the virial radius during the
streaming process. Finally, since streaming is much more efficient for
the CRps, we can ignore this effect for the CRes.

@@

\SPO{please check the following:} To order of magnitude, the
momentum-space diffusion coefficient due to second-order Fermi-II
acceleration scales as
\begin{eqnarray}
  D_{pp} \propto p\dot{p}
  \propto p^2\langle kc\rangle_{\mathcal{W}} \left(\frac{\Vph}{c}\right)^2,
\label{eq:dpp_oom}
\end{eqnarray}
since the force on a particle due to Fermi-II acceleration scales as
$\dot{p}\sim p/\tau\sim p \langle kc\rangle_{\mathcal{W}} (\Vph/c)^2$
where $\langle kc\rangle_{\mathcal{W}} (\Vph/c)^2$ is the wave
energy-averaged wave-particle interaction rate. It can be shown that
the particle pitch-angle averaged momentum-diffusion coefficient of
isotropic particles that couple to fast magnetosonic modes via TTD
resonance is \citep[][ Eqn. 47]{brunetti07}:
\begin{eqnarray}
  D_{pp}(p,t) = \frac{\upi}{16} \frac{p^2}{\rho c}
  \left\langle\frac{\beta |B_k|^2}{16 \upi \,W}\right\rangle
  I_\theta
  \int_{k_\rmn{cut}}\mathcal{W}(k)k\,d k\,,
\label{eq:dpp}
\end{eqnarray}
where $\beta$ is the thermal-to-magnetic pressure ratio, and $c$
is the speed of light. The energy density $W$ of a mode in a
magnetized plasma stems from both electromagnetic fields and resonant
particles. For a high-$\beta$ plasma, the pitch angle averaged ratio of
beta-weighted magnetic-to-total energy density saturates to $\langle\beta
|B_k|^2/2W\rangle\approx 10^{1.4}$ (see Figure 2 in
\citealt{brunetti07}). The pitch angle of the CR momentum with the
magnetic field orientation is given by $\theta$, and
\begin{equation}
  \label{eq:I_theta}
  I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
    |\cos \theta | }}
\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2.
\end{equation}
Here $V_\rmn{ph}$ is the phase velocity of the fast magnetosonic waves
given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a
sound speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As
in \cite{brunetti07}, we initially assume that the velocity of
turbulent eddies is $V_0\approx 0.47 c_\rmn{s}$ throughout the
cluster. This gives a turbulent acceleration time scale, $\tau_{D} =
p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM (see
Tab.~\ref{tab:timescales} for more details).

@@

The profile of injected turbulence depends on the details of the
merger such as time during the merger, the impact parameter, the
merger mass ratio, and the degree of cluster anisotropy
\citep{2015ApJ...800...60M}. We parametrize these uncertainties and
assume that it scales with the thermal energy density to some
power. Hence we assume volumetric injection rate of turbulent energy,
$I_0\propto \epsilon_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
normalization by requiring that the turbulent energy in compressible
modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
radio halo.\footnote{Simulations show that the compressible modes
  contribute a factor $0.2-0.4$ to the total turbulent energy
  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
  total turbulent energy, which can be decomposed into a slenoidal and
  compressible component, is typically $\sim15-70$\% of the thermal
  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
  our adopted value of $X_\rmn{tu}$.} In this work we investigate
different spatial models for injected turbulence. With the above
choice of normalization, the turbulent energy density becomes
$\epsilon_\rmn{turb} \propto
\epsilon_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
\Mprimary (see Figure~\ref{fig:turb} for visualization). \CP{These
  models and scaling indices are not well motivated here, they would
  better fit into the results section.}

Note that in previous work on the Coma cluster, $\epsilon_\rmn{turb}
\propto \epsilon_\rmn{th}$ was adopted which roughly corresponds to
$\alpha_\rmn{tu}= 1$ \citep{brunetti12} and together with the
different distributions for seed CRes constitute the main differences
compared to our work. Our flatter turbulent profiles are motivated by
fits to cosmological simulations
\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V,2012ApJ...758...74B}
and the range indicates uncertainties of the turbulent profile in
Coma. Future observations (by Astro-H) and simulations will help to
clarify this issue. Provided dissipation of turbulence in the ICM is
collisionless, turbulent cascades of compressible modes become
suppressed when thermal and relativistic particles resonantly interact
with magnetosonic waves via TTD on a timescale $\Gamma^{-1}$ that
approaches the cascading timescale given by $\tau_{kk} \approx
k^2/D_{kk}$. Thus, the cascade is suppressed for wave numbers above
\begin{equation}
\label{eq:kc}
  k_\rmn{cut} \approx \frac{81}{14} \frac{I_0}{\rho \langle \Vph \rangle}
  \left(\frac{\langle\sum_i \Gamma_i(k,\theta)\rangle}{k}\right)^{-2}\,,
\end{equation}
where $2\upi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
effective mean free path for CRs, unless plasma instabilities can
mediate interactions between turbulence and particles on smaller
scales \citep{brunetti11}.

@@

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
  \caption{The ratio of turbulent-to-thermal energy densities (solid
    lines) and cumulative energies (dotted lines) in our three
    models. The energy densities are parametrized as
    $\epsilon_\rmn{turb} \propto
    \epsilon_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
    normalized such that the total turbulent energy in compressible
    modes $E_\rmn{turb}$ for each scenario makes up about 20\% of the
    total thermal energy $E_\rmn{th}$ inside the radio halo
    ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
    the uncertainty in the cluster turbulence and are motivated by the
    cosmological simulation in
    \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}
  \label{fig:turb}
\end{figure}

@@

\subsection{Scaling relations for turbulent reacceleration}
To understand the radial dependence of the diffusion constant we
investigate how $D_\rmn{pp}$ scales with different parameters. This is
crucial in order to identify important parameters, and understand the
profile of reaccelerated CRs and radio emission. Combining
Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e} we find that 
\begin{equation}
  \label{eq:Dpp_scaling}
  D_\rmn{pp}\propto I_0/\rho c_s \propto 
X_\rmn{tu}^2k_0\epsilon_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}\,.
\end{equation}
Here we immediately see that if the turbulent profile trace the
thermal energy (i.e. $\alpha_\rmn{tu}=1$), the square root of
temperature alone determines the diffusion constant. We also see that
$D_\rmn{pp}$ is much more sensitive to $X_\rmn{tu}$ than $k_0$.

During reacceleration the CRps approximately gain a factor 
\begin{equation}
  \label{eq:Creacc}
  \Delta C_\rmn{reacc.} \sim
  \exp{\left[\frac{(2+\alpha)(\alpha+1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,,
\end{equation}
if injection and cooling are neglected. The reaccelerated CRs are then
exponentially dependent on $\tau_D\sim 1/D_\rmn{pp}$ as long as $\tau_D
\lesssim \tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration
of reacceleration of the merger which we assume to be 650~Myrs long.

In Figure~\ref{fig:tauD} we show how the turbulent reacceleration
timescales in our three models scale with radius. As expected, the
\Mprimary model with $\alpha_\rmn{tu}=0.88$ has the flattest profile
with $\tau_D\approx0.4\,\rmn{Gyr}$, where the small dip at large
radius driven by the decrease in thermal energy density. The
\Mflatturb model has the the flattest turbulent profile parameterized
by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_D$
profile. Note that a fixed reacceleration timescale is required to
explain the observations at each radius and for each model (see also
Table~\ref{tab:timescales}). This allows us to interchange the value
of uncertain parameters $\tau_\rmn{cl} \sim X_\rmn{tu}^2 \sim k_0$,
i.e. a longer reacceleration duration have to be compensated by
lowering the level of turbulence or increasing the physical injection
scale of turbulence to keep $\tau_D$ constant.

@@

\subsection{Spherically symmetric models}
In this section we develop a simple framework that will be used to
test the robustness of our models to the critical parameters for CRs
and turbulence in section~\ref{sect:param_comp}. Here we do not follow
single Lagrangian particles in the cluster, instead we use a more
simple approach where we solve the Fokker-Planck equation in static
spherical shells for injection, reacceleration, and losses of the
CRs. Once the CRs have been reaccelerated for $\tau_\rmn{cl} =
650\,\rmn{Myr}$, we calculate the radio emission and compare the
profile and spectra for different parameterizations.

We adopt both the density \citep{1992A&A...259L..31B} and temperature
profiles \citep{2009ApJ...696.1886B,2001A&A...365L..67A} derived from
X-ray observations of the Coma cluster. They are given by:
\begin{eqnarray}
n_e &=& \frac{3.4\times10^{-3}}{\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{1.125}}\nonumber\\
k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32}\,.
\end{eqnarray}
The virial and core radii of Coma are given by $R_{200} =
2300\,\rmn{kpc}$ and $R_{\rmn{c}} = 294\,\rmn{kpc}$, respectively.
The bulk of the CRps are injected by relatively low Mach number shocks
and parameterized by $f_\rmn{CRp,inj}(p) =
C_\rmn{CRp,inj}\,p^{-2.5}$. The CRps trace the thermal gas with
$C_\rmn{CRp,inj} \propto \epsilon_\rmn{th}^{\alpha_\rmn{CR,spat}}$,
where the normalization is fixed by assuming that the injected CR
energy in the last 650~Myrs make up 0.03\% of the thermal energy
inside the virial radius, i.e.
$\int_0^{R_{200}}\epsilon_\rmn{CRp,inj} \rmn{d}
V\left(\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V\right)^{-1} =
0.0003$. The spectrum of the initial CRp distribution is determined by
the steady state between injection and cooling,
\begin{equation}
 f_\rmn{CRp,0} \propto \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where we fix the normalization by requiring
$\int_0^{R_{200}}\epsilon_\rmn{CRp,0}
\rmn{d}V\left(\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V\right)^{-1} =
0.003$. Similarly, the initial CRe distribution is given by the steady
state between cooling (Coulomb, inverse Compton, and synchrotron) and
injection of secondary CRes from $f_{CRp,0}$. We also include the
continuous injection of secondary CRes during $\tau_\rmn{cl}$. The
compressible turbulence responsible for reaccelerating both the CRps
and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_{\rmn{e}}
T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_\rmn{pp}$ is
calculated for each radial bin using
Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters and assumptions
are similar to what is used for our simulated cluster.

@@

\subsection{Radio profile}
In Fig.~\ref{fig:sync_profile}, we find that all three scenarios in
which the seeds undergo Fermi-II reacceleration can reproduce the Coma
RH profile at 352~MHz. In the panel {\it Brunetti et al. (2012)} we
show that without CR streaming or a flat turbulent profile, our
simulations of reaccelerated CRs produce radio profiles that are too
steep. Indeed, even using the assumptions of previous work -- where
complete freedom in the seed population was allowed -- it is not
possible to reproduce observations in both frequencies in any
model. Note that decreasing acceleration efficiency with radius does
not change this conclusion much because of the weak radial dependence
of $D_\rmn{pp}(R)\propto
\epsilon_\rmn{th}(R)^{\alpha_\rmn{tu}-1}\sqrt{T(R)}$. This
signals that the problem is generic and requires either additional
modifications to the plasma physics of acceleration or a better
understanding of potential observational systematics. In addition
there are differences in the simulated density and temperature
profiles in comparison to the observed profile in Coma that impact the
CR abundance as well as cooling and reacceleration.

>>>>

\renewcommand{\vec}{\ensuremath{\mathbfit}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Vph}{V_\mathrm{ph}}
\newcommand{\mug}{\umu G}
\newcommand{\RH}{R_\rmn{RH}}
\newcommand{\bvel}{\ensuremath{\boldsymbol{\varv}}}
\newcommand{\bnabla}{\ensuremath{\boldsymbol{\nabla}}}
\newcommand\eb{\epsilon_\rmn{B}}
\newcommand{\dps}{\displaystyle}
\newcommand{\p}{\rmn{p}}
\newcommand{\kB}{k_{\rmn{B}}}
\newcommand{\eps}{\varepsilon}

@@

During post-processing of our Coma-like cluster simulation, we solve
the Fokker-Planck equation over a redshift interval from $z=5$ to
0. The simulated cluster undergoes a major merger over the last
1-2~Gyrs that is thought to inject large turbulent eddies. Following
standard approaches
\citep{brunetti07,brunetti11,2004ApJ...614..757Y,2015ApJ...800...60M}
we assume that about one Gyr after core passage the fields have
decayed down to the smallest scales where reacceleration is most
efficient ($D_{pp}\sim k_\rmn{cut}$) and the radio halo turns on
shortly after. Note that the exact decay time of the turbulens is of
minor importance, since the thermal and CR quantities are very similar
a few 100 Myrs before and after $z=0$ where we have chosen to evaluate
the simulations. This delay naturally explains why giant radio halos
are only seen in a fraction of all merging clusters.

In all our calculations we assume that turbulent reacceleration
efficiently accelerates particles for $\tau_\rmn{cl}\sim650$~Myrs
(which is roughly the cascade time on which turbulence is damped) and
that during this turbulent phase CR streaming and spatial diffusion
can be neglected. In our \Mstream model, CR streaming and diffusion
are incorporated separately during kinematically quiescent times that
precede the merger. As a result, flat CRp profiles are produced on
relatively short timescales ($\sim 0.1-0.5$ Gyr). This allows us to
implicitly solve for CR streaming in our calculations, where we adopt
a toy model that enforce a flat CRp profile at all quiescent times
\citep{wiener13}. We assume that CRs cannot stream significantly past
perpendicular $B$-fields at the accretion shock, so that the total
number of CRs is conserved within the virial radius during the
streaming process. Finally, since streaming is much more efficient for
the CRps, we can ignore this effect for the CRes.

@@

\SPO{please check the following:} To order of magnitude, the
momentum-space diffusion coefficient due to second-order Fermi-II
acceleration scales as
\begin{eqnarray}
  D_{pp} \sim p\dot{p}
  \sim p^2\langle kc\rangle_{\mathcal{W}} \left(\frac{\Vph}{c}\right)^2,
\label{eq:dpp_oom}
\end{eqnarray}
since the force on a particle due to Fermi-II acceleration scales as
$\dot{p}\sim p/\tau\sim p \langle kc\rangle_{\mathcal{W}} (\Vph/c)^2$
where $\langle kc\rangle_{\mathcal{W}} (\Vph/c)^2$ is the wave
energy-averaged wave-particle interaction rate. It can be shown that
the particle pitch-angle averaged momentum-diffusion coefficient of
isotropic particles that couple to fast magnetosonic modes via TTD
resonance is \citep[][ Eqn. 47]{brunetti07}:
\begin{eqnarray}
  D_{pp}(p,t) = \frac{\upi}{16} \frac{p^2}{\rho c}
  \left\langle\frac{\beta |B_k|^2}{16 \upi \,W}\right\rangle
  I_\theta
  \int_{k_\rmn{cut}}\mathcal{W}(k)k\,d k\,,
\label{eq:dpp}
\end{eqnarray}
where $\beta$ is the thermal-to-magnetic pressure ratio, and $c$
is the speed of light. The energy density $W$ of a mode in a
magnetized plasma stems from both electromagnetic fields and resonant
particles. For a high-$\beta$ plasma, the pitch angle averaged ratio of
beta-weighted magnetic-to-total energy density saturates to $\langle\beta
|B_k|^2/2W\rangle\approx 10^{1.4}$ (see Figure 2 in
\citealt{brunetti07}). The pitch angle of the CR momentum with the
magnetic field orientation is given by $\theta$, and
\begin{equation}
  \label{eq:I_theta}
  I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
    |\cos \theta | }}
\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2.
\end{equation}
Here $V_\rmn{ph}$ is the phase velocity of the fast magnetosonic waves
given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a
sound speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As
in \cite{brunetti07}, we initially assume that the velocity of
turbulent eddies is $V_0\approx 0.47 c_\rmn{s}$ throughout the
cluster. This gives a turbulent acceleration time scale, $\tau_{D} =
p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM (see
Tab.~\ref{tab:timescales} for more details).

@@

The profile of injected turbulence depends on the details of the
merger such as time during the merger, the impact parameter, the
merger mass ratio, and the degree of cluster anisotropy
\citep{2015ApJ...800...60M}. We parametrize these uncertainties and
assume that it scales with the thermal energy density to some
power. Hence we assume volumetric injection rate of turbulent energy,
$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
normalization by requiring that the turbulent energy in compressible
modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
radio halo.\footnote{Simulations show that the compressible modes
  contribute a factor $0.2-0.4$ to the total turbulent energy
  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
  total turbulent energy, which can be decomposed into a slenoidal and
  compressible component, is typically $\sim15-70$\% of the thermal
  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
  our adopted value of $X_\rmn{tu}$.} In this work we investigate
different spatial models for injected turbulence. With the above
choice of normalization, the turbulent energy density becomes
$\eps_\rmn{turb} \propto
\eps_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
\Mprimary (see Figure~\ref{fig:turb} for visualization). \CP{These
  models and scaling indices are not well motivated here, they would
  better fit into the results section.}

Note that in previous work on the Coma cluster, $\eps_\rmn{turb}
\propto \eps_\rmn{th}$ was adopted which roughly corresponds to
$\alpha_\rmn{tu}= 1$ \citep{brunetti12} and together with the
different distributions for seed CRes constitute the main differences
compared to our work. Our flatter turbulent profiles are motivated by
fits to cosmological simulations
\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V,2012ApJ...758...74B}
and the range indicates uncertainties of the turbulent profile in
Coma. Future observations (by Astro-H) and simulations will help to
clarify this issue. Provided dissipation of turbulence in the ICM is
collisionless, turbulent cascades of compressible modes become
suppressed when thermal and relativistic particles resonantly interact
with magnetosonic waves via TTD on a timescale $\Gamma^{-1}$ that
approaches the cascading timescale given by $\tau_{kk} \approx
k^2/D_{kk}$. Thus, the cascade is suppressed for wave numbers above
\begin{equation}
\label{eq:kc}
  k_\rmn{cut} \approx \frac{81}{14} \frac{I_0}{\rho \langle \Vph \rangle}
  \left(\frac{\langle\sum_i \Gamma_i(k,\theta)\rangle}{k}\right)^{-2}\,,
\end{equation}
where $2\upi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
effective mean free path for CRs, unless plasma instabilities can
mediate interactions between turbulence and particles on smaller
scales \citep{brunetti11}.

@@

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
  \caption{The ratio of turbulent-to-thermal energy densities (solid
    lines) and cumulative energies (dotted lines) in our three
    models. The energy densities are parametrized as
    $\eps_\rmn{turb} \propto
    \eps_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
    normalized such that the total turbulent energy in compressible
    modes $E_\rmn{turb}$ for each scenario makes up about 20\% of the
    total thermal energy $E_\rmn{th}$ inside the radio halo
    ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
    the uncertainty in the cluster turbulence and are motivated by the
    cosmological simulation in
    \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}
  \label{fig:turb}
\end{figure}

@@

\subsection{Scaling relations for turbulent reacceleration}

\SPO{should this be moved to the preceeding section?}
To understand the radial dependence of the diffusion constant we
investigate how $D_{pp}$ scales with different parameters. This is
crucial in order to identify important parameters, and understand the
profile of reaccelerated CRs and radio emission. Combining
Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e} we find that 
\begin{equation}
  \label{eq:Dpp_scaling}
  D_{pp}\propto \frac{I_0}{\rho c_{\rmn{s}}} \propto 
X_\rmn{tu}^2k_0\eps_\rmn{th}^{\alpha_\rmn{tu}-1}\sqrt{T}\,.
\end{equation}
Here we immediately see that if the turbulent profile traces the
thermal energy (i.e. $\alpha_\rmn{tu}=1$), the square root of
temperature determines the diffusion constant. We also see that
$D_{pp}$ is much more sensitive to the turbulent energy content
$X_\rmn{tu}$ in comparison to the injection scale $k_0$.

During reacceleration, the CRps increase their normalization
approximately by the factor
\begin{equation}
  \label{eq:Creacc}
  \delta C_\rmn{reacc.} \sim 
  \exp{\left[\frac{(2+\alpha)(\alpha+1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,,
\end{equation}
if injection and cooling are neglected. The reaccelerated CRs depend
exponentially on $\tau_D\sim 1/D_{pp}$ as long as $\tau_D \lesssim
\tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration of
reacceleration of the merger which we assume to be 650~Myrs long.

\CP{Again the logic is skewed here: these models are derived from the
  spatial profile of the synchrotron emission in Sect. 4. Hence
  $D_{pp}$ should be discussed after those have been introduced.}  In
Figure~\ref{fig:tauD} we show how the turbulent reacceleration
timescales in our three models scale with radius. As expected, the
\Mprimary model with $\alpha_\rmn{tu}=0.88$ has the flattest profile
with $\tau_D\approx0.4\,\rmn{Gyr}$, where the small dip at large
radius driven by the decrease in thermal energy density. The
\Mflatturb model has the the flattest turbulent profile parameterized
by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_D$
profile. Note that a fixed reacceleration timescale is required to
explain the observations at each radius and for each model (see also
Table~\ref{tab:timescales}). This allows us to interchange the value
of uncertain parameters $\tau_\rmn{cl} \sim X_\rmn{tu}^2 \sim k_0$,
i.e. a longer reacceleration duration have to be compensated by
lowering the level of turbulence or increasing the physical injection
scale of turbulence to keep $\tau_D$ constant.

@@

\subsection{Spherically symmetric models}
In this section we develop a simplified framework that will be used to
test the robustness of our models with respect to the critical
parameters for CRs and turbulence in Section~\ref{sect:param_comp}. In
order to quickly explore parameter space, we we solve the
Fokker-Planck equation in static spherical shells for injection,
reacceleration, and losses of the CRs, i.e., we neglect the Lagrangian
trajectories during the re-acceleration time.  Once the CRs have been
reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$, we calculate the
radio emission and compare the profile and spectra for different
parameterizations.

We adopt both the density \citep{1992A&A...259L..31B} and temperature
profiles \citep{2009ApJ...696.1886B,2001A&A...365L..67A} derived from
X-ray observations of the Coma cluster. They are given by:
\begin{eqnarray}
n_e &=& \frac{n_0}{\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{1.125}}\nonumber\\
k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32}\,,
\end{eqnarray}
with $n_0=3.4\times10^{-3}\,\rmn{cm}^{-3}$.  The virial and core radii
of Coma are given by $R_{200} = 2300\,\rmn{kpc}$ and $R_{\rmn{c}} =
294\,\rmn{kpc}$, respectively.

\AP{Can you please provide references for the following:} The bulk of the
CRps are injected by relatively low Mach number shocks and
parameterized by $f_\rmn{p,inj}(p) = C_\rmn{inj}\,p^{-2.5}$. The
CRps trace the thermal gas with $C_\rmn{inj} \propto
\eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$, where the normalization is
fixed by assuming that the injected CR energy in the last 650~Myrs
make up 0.03\% of the thermal energy inside the virial radius, i.e.
$\int_0^{R_{200}}\eps_\rmn{p,inj} \rmn{d}
V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
0.0003$. The spectrum of the initial CRp distribution is determined by
the steady state between injection and cooling,
\begin{equation}
 f_\rmn{p,0} \propto \frac{\int_p^\infty f_\rmn{p,inj}(p') 
\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where we fix the normalization by requiring
$\int_0^{R_{200}}\eps_\rmn{p,0}
\rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
0.003$. \AP{not 0.0003?} Similarly, the initial CRe distribution is
given by the steady state between cooling (Coulomb, inverse Compton,
and synchrotron) and injection of secondary CRes from $f_\rmn{p,0}$. We
also include the continuous injection of secondary CRes during
$\tau_\rmn{cl}$. The compressible turbulence responsible for
reaccelerating both the CRps and CRes is parameterized by $I_0 \propto
X_\rmn{tu} (n_{\rmn{e}} T)^{\alpha_\rmn{tu}}$. The diffusion constant
$D_{pp}$ is calculated for each radial bin using
Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters and assumptions
are similar to what is used for our simulated cluster.

@@

\subsection{Radio profile}
In Fig.~\ref{fig:sync_profile}, we find that all three scenarios in
which the seeds undergo Fermi-II reacceleration can reproduce the Coma
RH profile at 352~MHz. In the panel {\it Brunetti et al. (2012)} we
show that without CR streaming or a flat turbulent profile, our
simulations of reaccelerated CRs produce radio profiles that are too
steep. Indeed, even using the assumptions of previous work -- where
complete freedom in the seed population was allowed -- it is not
possible to reproduce observations in both frequencies in any
model. Note that decreasing acceleration efficiency with radius does
not change this conclusion much because of the weak radial dependence
of $D_\rmn{pp}(R)\propto
\eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}\sqrt{T(R)}$. This
signals that the problem is generic and requires either additional
modifications to the plasma physics of acceleration or a better
understanding of potential observational systematics. In addition
there are differences in the simulated density and temperature
profiles in comparison to the observed profile in Coma that impact the
CR abundance as well as cooling and reacceleration.
